### 2024-07-22 data-visualization.qmd
20240722 - add rug plot

### Histogram with Overlaid Density Plot {#sec-histogramDensity}

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points)
) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  theme_classic()
```

>>>>

### Histogram with Overlaid Density and Rug Plot {#sec-histogramDensity}

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = fantasy_points)
) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  geom_rug() +
  theme_classic()
```
